DeepSphere: a graph-based spherical CNN

### 2019-11-14 main.tex
add climate to spectrum figure
update kernels

\todo{
TODO:
\begin{itemize}
	\item PSD of climate data: how does it compare to cosmo and 3D objects? Climate data on spectrum plot. \nati{I would drop this}
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, fields, functions. Irregular, uneven. Coarsening, down-sampling. Sample, vertex, node, pixel, point.
	\item check English vs American English
	\item Explain heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison. \nati{Not sure what you mean here.}
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item Compute the invariance error of the whole NNs (before and after training, invariance can be learned). Add it with equivariance error of the convolution to \tabref{cosmo}. \nati{I guess we are not doing that}
	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
\end{itemize}
}

@@

% 2) explain our approach
We chose a different approach and take inspiration from \citet{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
\begin{equation} \label{eqn:weights:belkin}
w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
\end{equation}
In practice, because of the exponential, most of the weights are very close to $0$. Hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid.

@@

		\caption{Normalized mean equivariance error \eqref{eq:mean equivariance error}. The number of pixels is $n = 4 s^2$ for the equiangular sampling and $n = 12 s^2$ for the HEALPix sampling.}
		\label{fig:equivariance_error}
	\end{minipage}
	\hfill
	\begin{minipage}{0.35\linewidth}
		\centering
		\includegraphics[width=\linewidth]{kernel_widths}
		\caption{Optimal kernel widths.}
		\label{fig:kernel_widths}
		\vspace{1em}
		\includegraphics[height=4.5em]{lamp_000018}
		\hfill
		\includegraphics[height=4.5em]{lamp_000018_sphere_nobar}
		\caption{3D object represented as a spherical depth map.}
		\label{fig:depthmap}
		\vspace{1em}
		\includegraphics[width=\linewidth]{spectrum}
		\caption{Power spectral densities.}
		\label{fig:spectrum}
	\end{minipage}
\end{figure}

>>>>

\todo{
TODO:
\begin{itemize}
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, fields, functions. Irregular, uneven. Coarsening, down-sampling. Sample, vertex, node, pixel, point.
	\item check English vs American English
	\item Explain heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison. \nati{Not sure what you mean here.}
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item Compute the invariance error of the whole NNs (before and after training, invariance can be learned). Add it with equivariance error of the convolution to \tabref{cosmo}. \nati{I guess we are not doing that}
	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
\end{itemize}
}

@@

% 2) explain our approach
We chose a different approach and take inspiration from \citet{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
\begin{equation} \label{eqn:weights:belkin}
w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
\end{equation}
In practice, because of the exponential, most of the weights are very close to $0$. Hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
In~\cite{perraudin2019deepspherecosmo}, the parameter $t$ was heuristically set to $0.5$ times the average squared distances over all connected pixels.
In this work, we decided to use a more refined method.
Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid. 
% We observe that with a small kernel size $t$, \cite{perraudin2019deepspherecosmo} would probably be more equivariant.

@@

		\caption{Normalized mean equivariance error \eqref{eq:mean equivariance error}. The number of pixels is $n = 4 s^2$ for the equiangular sampling and $n = 12 s^2$ for the HEALPix sampling.}
		\label{fig:equivariance_error}
	\end{minipage}
	\hfill
	\begin{minipage}{0.35\linewidth}
		\centering
		\includegraphics[width=\linewidth]{kernel_widths}
		\caption{Optimal kernel widths. For comparizon, we added the kernel used by~\cite{perraudin2019deepspherecosmo}}
		\label{fig:kernel_widths}
		\vspace{1em}
		\includegraphics[height=4.5em]{lamp_000018}
		\hfill
		\includegraphics[height=4.5em]{lamp_000018_sphere_nobar}
		\caption{3D object represented as a spherical depth map.}
		\label{fig:depthmap}
		\vspace{1em}
		\includegraphics[width=\linewidth]{spectrum}
		\caption{Power spectral densities.}
		\label{fig:spectrum}
	\end{minipage}
\end{figure}
